Supplementary material for Sequential rank agreement methods for comparison of ranked lists

### 2023-08-27 latex/biosts3-supp.tex
Updated documentation

\documentclass[oupdraft]{bio}
%\usepackage[colorlinks=true, urlcolor=citecolor, linkcolor=citecolor, citecolor=citecolor]{hyperref}
% \documentclass[12pt,a4paper]{article}
\pdfoutput=1
\usepackage[utf8]{inputenc}
%\usepackage[]{graphicx}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage[]{color}
%\usepackage{subcaption}
% \usepackage{natbib}
%\usepackage{xspace}
%\usepackage{calc}
% \usepackage[noae]{Sweave}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
% \usepackage{enumitem}

@@

This document provides proofs of the theorem and corollary shown in the main manuscript.

@@

>>>>

\documentclass[oupdraft]{bio}
%\usepackage[colorlinks=true, urlcolor=citecolor, linkcolor=citecolor, citecolor=citecolor]{hyperref}
% \documentclass[12pt,a4paper]{article}
\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\usepackage[]{graphicx}
%\usepackage{amsmath}
%\usepackage{amssymb}
%\usepackage[]{color}
%\usepackage{subcaption}
% \usepackage{natbib}
%\usepackage{xspace}
%\usepackage{calc}
% \usepackage[noae]{Sweave}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
% \usepackage{enumitem}

@@

This document provides proofs of the theorem and corollary shown in the main manuscript as well as details about the algorithm for incomplete lists.

@@

\section{Algorithm for sequential rank agreement for incomplete lists}
\label{sec:appA}

\begin{algorithm}
\caption{Sequential rank agreement algorithm for incomplete lists}
\label{sra-algorithm}
\begin{algorithmic}[1]
  \Procedure{Incomplete list rank agreement}{} \State Let $B$ be the number
  of permutations to use \For{each $b \in B$} \For{each list
    $l \in L$}
  \State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1.7cm}{Permute
    the unassigned ranks, $\{d_l+1, \ldots, P\}$, and assign them
    randomly to the items \emph{not} found in the list, i.e.,
    $\Lambda^\complement=X\setminus\Lambda_l$. Combine the
    result with $\Lambda_l$ to fill out the list.}
\EndFor
\State \parbox[t]{\dimexpr\linewidth-\algorithmicindent-1cm}{Let sra($b$) be the sequential rank agreement computed from the
filled out lists.}
\EndFor
\State Return element-wise averages across all $B$ permutations of sra($b$).
\EndProcedure
\end{algorithmic}
\end{algorithm}
